Differential cultural reproduction of skill level and mental templates in Late Acheulean handaxe morphology: Archaeological and experimental insights

### 2022-12-31 manuscript/manuscript.Rmd
added a few more references.

The archaeological site of Boxgrove is located in the former Eartham quarry, Boxgrove, West Sussex, featuring a long sequence of Middle Pleistocene deposits [@roberts1998; @pope2020]. This 500-ka-old site has documented exceedingly rich details of Lower Paleolithic hominin subsistence behaviors [@smith2012; @smith2013] and their paleoenvironmental contexts [@holmes2010]. In addition to the presence of one of the earliest hominin fossil [tentatively assigned to *Homo heidelbergensis*, @hillson2010; @lockey2022] and bone assemblages with anthropogenic modifications in northern Europe [@bello2009], Boxgrove is mostly known for its large sample size of Late Acheulean-style flint handaxes and the high skill level reflected in their manufacture (**Figure** \@ref(fig:photos)). As such, it has received wide research attention in the past two decades regarding the relationships between technology, cognition, and skills [@stout2014; @iovita2011; @iovita2017; @shipton2015; @garcía-medrano2019; @keyHandaxeShapeVariation2019]. To identify the morphological manifestation of knappers' skill level in our study, we selected a complete handaxe assemblage (n=326) previously analyzed and reported in digital formats by Iovita and McPherron [-@iovita2011], which is currently curated at the Franks House of the British Museum [@iovita2017]. The digital photographs are taken of each handaxe at a 90$^{\circ}$ angle, which was oriented with the tip to the right of the photos, and the camera faces the most convex surface of the handaxe [@iovita2011].

>>>>

The archaeological site of Boxgrove is located in the former Eartham quarry, Boxgrove, West Sussex, featuring a long sequence of Middle Pleistocene deposits [@roberts1998; @pope2020]. This 500-ka-old site has documented exceedingly rich details of Lower Paleolithic hominin subsistence behaviors [@smith2012; @smith2013] and their paleoenvironmental contexts [@holmes2010; @preece2022]. In addition to the presence of one of the earliest hominin fossil [tentatively assigned to *Homo heidelbergensis*, @hillson2010; @lockey2022; @roberts1994] and bone assemblages with anthropogenic modifications in northern Europe [@bello2009], Boxgrove is mostly known for its large sample size of Late Acheulean-style flint handaxes and the high skill level reflected in their manufacture (**Figure** \@ref(fig:photos)). As such, it has received wide research attention in the past two decades regarding the relationships between technology, cognition, and skills [@stout2014; @iovita2011; @iovita2017; @shipton2015; @garcía-medrano2019; @keyHandaxeShapeVariation2019]. To identify the morphological manifestation of knappers' skill level in our study, we selected a complete handaxe assemblage (n=326) previously analyzed and reported in digital formats by Iovita and McPherron [-@iovita2011], which is currently curated at the Franks House of the British Museum [@iovita2017]. The digital photographs are taken of each handaxe at a 90$^{\circ}$ angle, which was oriented with the tip to the right of the photos, and the camera faces the most convex surface of the handaxe [@iovita2011].
